plottingScript

### 2023-04-05 analyses/plotter.Rmd
updated text

g<-plot_grid(pt, legend,ncol = 1, rel_heights = c(1, .1), rel_widths = c(3, .4))
pdf(file="figures/megaPlot.pdf",width=16,height=9)
g
dev.off()
```

@@

pdf(file="figures/megaTable.pdf",width=14,height=13)
cowplot::plot_grid(cFlex,mFlex,fFlex,pFlex,ncol=1)
dev.off()

@@

pdf(file="figures/winTable.pdf",width=12,height=6)
cowplot::plot_grid(cwtab,mwtab,fwtab,pwtab,ncol=2)
dev.off()

@@

```{r complexHazard}

@@

pdf(file="figures/ComplexPopTime.pdf",width=8,height=6)
a
dev.off()

>>>>

g<-plot_grid(pt, legend,ncol = 1, rel_heights = c(1, .1), rel_widths = c(3, .4))
pdf(file="../StatPaper/figures/megaPlot.pdf",width=16,height=9)
g
dev.off()
```

@@

pdf(file="../StatPaper/figures/megaTable.pdf",width=14,height=13)
cowplot::plot_grid(cFlex,mFlex,fFlex,pFlex,ncol=1)
dev.off()

@@

pdf(file="../StatPaper/figures/winTable.pdf",width=12,height=6)
cowplot::plot_grid(cwtab,mwtab,fwtab,pwtab,ncol=2)
dev.off()

@@

```{r complexHazard,eval=FALSE}

@@

pdf(file="../StatPaper/figures/ComplexPopTime.pdf",width=8,height=6)
a
dev.off()
